<small> Supplementary materials for the main submission entitled - <br><br> Clustering time series based on probability distributions across temporal granularities

### 2021-11-09 paper-supplementary.Rmd
sindex for 353 customers update

## Clustering on 350 customers

@@

id <- c(first_lot[-1], mds_data$name[nrow(mds_data)])

@@

library(fpc)
library(cluster)
k = array()
for(i in 5:50)
{
  group <- f %>% hclust (method = "ward.D") %>% cutree(k=i)
  p <- cluster.stats(f, clustering = group, silhouette = TRUE)
  k[i]=p$sindex
}

ggplot(k %>% as_tibble %>% mutate(k = row_number()), aes(x=k, y = value)) + geom_line() + scale_x_continuous(breaks = seq(2, 50, 2))

>>>>

@@

id <- c(first_lot[-1], mds_data$name[nrow(mds_data)])
```

```{r opt-clust-350, fig.cap = "Cluster separation for the 353 customers across the number of clusters is shown. When the cluster size changes from 17 to 18, the separation index drops sharply and then flattens out, resulting in the appearance of the elbow. Hence, when grouping the 353 customers, the number of clusters is taken to be 17."}

@@

k = array()
for(i in 5:50)
{
  group <- f %>% hclust (method = "ward.D") %>% cutree(k=i)
  p <- cluster.stats(f, clustering = group, silhouette = TRUE)
  k[i]=p$sindex
}

ggplot(k %>% as_tibble %>% mutate(k = row_number()), aes(x=k, y = value)) + geom_line() + scale_x_continuous(breaks = seq(2, 50, 2), minor_breaks = 1) + xlab("number of clusters") + ylab ("separation index")
```

```{r}
